Lessons Learned from Differential Testing JS Engines

### 2018-07-06 paper/paper.tex
pass on reviews

\subsection{Seed JS files}~We considered in our study test suites
associated with all four JS engines we analyzed
(section~\ref{sec:methodology:engines}). In addition, we mined test
suites from other repositories based on the following criteria:
\begin{itemize}
  \item The project must be an open-source project and at least 1K stars from community.
  \item The repository must have JavaScript tests included.
  \item The tests should be plug-and-play and/or easy
    integration.\Mar{not clear what you mean}
\end{itemize}

Figure~\ref{fig:query} illustrates the Github API query\Fix{cite} we
used to find projects with JS files\Mar{why the query is so specific?
  as per ``q=javascript-engine''? Need to be consistent to what you
  are saying an coherent to what you actually did.}. The query sorts
results in descending order in the number of stars\Mar{sorting is only
  relevant if you set a limit on the number of projects you will
  analyze. What limit is that?}. The resulting list includes a total
of \Fix{XX} projects. A total of \Fix{...}  projects remained after
removing projects that \Fix{...}. Table~\ref{tab:test-suites} shows
the JS sources we considered for each of these selected
projects..\Mar{identify the sources assoc. with the four analyzed
  engines. you said in the first sentence this is one source.} Overall, we found a total of \totfiles{} JS
files.\Mar{Briefly explain these sources.}

\begin{figure}[h]
  \centering
  \begin{lstlisting}
https://api.github.com/search/repositories?q=javascript-engine+stars:>=1000&sort=stars
  \end{lstlisting}
  \caption{\label{fig:query}
  Query to the GitHub API for JS engines projects that contain over 1K stars.\Fix{fix query}
  }
\end{figure}

@@

It is worth noting that some projects use distinct frameworks for
testing and require external libraries to run their testing
suites. For these projects, we needed to make small changes in the testing
infrastructure to be able to uniformly run tests in all
engines.\Mar{not entirely clear what you did to support
  this.$\rightarrow$}We aimed to use only the JS file with minor fixes
to support our environment. These fixes are composed by an assertion
function that throws an Error that we can capture by our
infraestruture.

@@

\subsection{Fuzzing versus No Fuzzing}
\Fix{nao entendi muito sobre essa subsection... 
seria explicacao do porque utilizar o fuzzing baseado nos nosso resultados?}
\Igor{
  Os engines JS mais populares foram arduamente testados ao longo dos últimos anos, 
  o sistema robusto nao significa que esta livre de bugs, ao contrario,
  estamos testando-o com simples entradas a partir de testes de regressao 
  de bugs previamente encontrados, porem estas entradas poderiam servir como seeds 
  para novos testcases. Partindo disso, realizar fuzzer em arquivos 
  existentes em projetos open-sources eh uma maneira de
  aumentar ainda mais a eficiencia destes engines, por exemplo o Google incentiva o 
  uso de fuzzers no seu ecossistema\cite{oss-fuzz,honggfuzz}.

>>>>

\subsection{Seed JS files}~We considered in our study test suites
associated with all four JS engines we analyzed
(section~\ref{sec:methodology:engines}). In addition, we mined test
suites from other repositories based on the following criteria:
\begin{itemize}
  \item The project must be an open-source project and at least 1K stars from community.
  \item The repository must have JavaScript tests included.
  \item It does not use external libraries 
\end{itemize}

Figure~\ref{fig:query} illustrates the Github API query\Fix{cite} we
used to find javascript engines projects defined by the keyword "javascript-engine". 
The resulting list includes a total of 33 projects.
A total of \Fix{...}  projects remained after
removing projects that \Fix{...}. Table~\ref{tab:test-suites} shows
the JS sources we considered for each of these selected
projects..\Mar{identify the sources assoc. with the four analyzed
  engines. you said in the first sentence this is one source.} Overall, we found a total of \totfiles{} JS
files.\Mar{Briefly explain these sources.}

\begin{figure}[h]
  \centering
  \begin{lstlisting}
https://api.github.com/search/repositories?q=javascript-engine+stars:>=1000
  \end{lstlisting}
  \caption{\label{fig:query}
  Query to the GitHub API for JS engines projects that contain over 1K stars.\Fix{fix query}
  }
\end{figure}

@@

It is worth noting that some projects use distinct frameworks for
testing and require external libraries to run their testing
suites. For these projects, we needed to make small changes in the testing
infrastructure to be able to uniformly run tests in all
engines.\Mar{not entirely clear what you did to support
  this.$\rightarrow$}\Igor{wip}We aimed to use only the JS file with minor fixes
to support our environment. These fixes are composed by an assertion
function that throws an Error that we can capture by our
infraestruture.

@@

\subsection{Fuzzing versus No Fuzzing}
\Igor{
  Para identificar a eficacia e eficiencia da nossa abordagem, 
  foi necessario identificar se seeds de diferentes engenhos 
  sao efetivos em

  Os engines JS mais populares foram arduamente testados ao longo dos últimos anos, 
  o sistema robusto nao significa que esta livre de bugs, ao contrario,
  estamos testando-o com simples entradas a partir de testes de regressao 
  de bugs previamente encontrados, porem estas entradas poderiam servir como seeds 
  para novos testcases. Partindo disso, realizar fuzzer em arquivos 
  existentes em projetos open-sources eh uma maneira de
  aumentar ainda mais a eficiencia destes engines, por exemplo o Google incentiva o 
  uso de fuzzers no seu ecossistema\cite{oss-fuzz,honggfuzz}.
